An efficient acyclic contact planner for multiped robots

### 2017-01-12 body/results.tex
[Results] darpa scenario

% !TEX root =  ../main.tex
\section{Results}
\label{sec:results}
In this Section we present some of the results obtained with our planner. The complete sequences computed are shown in the companion video.
Specifically, we demonstrate the planner for two really different robots, in a large variety of environments: the humanoid HRP-2 and the quadruped HyQ.
Finally, a last example suggests possible applications to dexterous manipulation.
At the end of the video, we validate our contact plans by exhibiting a solution to the interpolation problem $\mathcal{P}_3$ for these scenarios.

At the end of this Section, we provide the \textit{interactive} computation times obtained in each case.
We also compare the times obtained with HRP-2 with respect to previous demonstrations.

@@

\subsection{Description of the scenarios}
In all the scenarios considered, the formulation of the problem is always the same:
a start and goal root configurations are provided as an input of the scenario.
The framework computes the initial contact configuration, and outputs a sequence of contact configurations connecting it to the goal.
In each scenario we detail the parameters chosen: the heuristics (either $h_{\textrm{\it EFORT}}$, $h_{vel}$ or $h_{w}$, and optionally the equilibrium robustness, all of which are defined in the Appendix~\ref{sec:heuristics}), and the constraints on the reachable workspaces (for instance in all the scenarios,
the reachable workspaces of the legs of HRP-2 are always required to intersect with the environment). 
%~ The companion video presents the complete contact sequence obtained in all these scenarios.

@@

\noindent\textbf{Heuristics:} The manipulability $h_w$ is chosen for the feet; $h_{\textrm{\it EFORT}}$ is chosen for the right arm.
Regarding equilibrium, the video demonstrates two sequences computed for two different threshold values of $b_0$: $0$ and $2$ (Figure~\ref{fig:stair_robust}).

\noindent\textbf{Observations:}
This scenario illustrates best the importance of the equilibrium-robustness criterion.
With a robust approach, more states are required to reach the last step (15 rather than 13 in average).
However, when the last step is reached by both feet, in the nonrobust case the contacts are extremely close to 
the cone limits (Figure~\ref{fig:stair_comp}).

The geometry of the environment is easily addressed by our planner, and the contact planning is several times faster than real time in this scenario.

Again, the interpolation motion between the contact steps is out of the scope of this paper. However it should be noted that the computed plan in this scenario has been executed successfully on the robot (\url{http://youtu.be/YjL-DBQgXwk#t=0m28s}).

\begin{figure}
  \centering
  %~ \includegraphics[width=0.6\linewidth]{figures/stair_robust}
  \begin{overpic}[width=0.5\linewidth]{figures/stair_robust}
		\put (17,5) {\small{\color{red}$b_0 = 0.23$}} 
		\put (79,5) {\small{\color{green}$b_0 = 6.16$}} 
		%~ \put (68,) {3.a)} 
		%~ \put (5,27) {3.b)} 
		%~ \put (37,27) {4.a)} 
		%~ \put (68,27) {4.b)} 
	\end{overpic}
  \caption{
           Evaluation of the robustness $b_0$ of two contact configurations. Although in equilibrium, the left configuration is on the verge of slipping.}
		   \label{fig:stair_comp}
\end{figure}

@@

\noindent\textbf{Observations:} The scenario illustrates well the acyclic aspect of the planning. For instance, in the four first frames of Figure~\ref{fig:standing}, we can see that the right foot
is moved twice, with the left foot in between, before the configuration allows HRP-2 to move its hand.
Because the contacts are tried in a FIFO manner, the fact that the output contact sequence is acyclic shows that a cyclic approach (with a finite state machine for instance) is not sufficient
for the computed path. The reason for this is not reachability, but equilibrium. The planning is slower than for the stair scenario (because the contact generation fails more),
though it remains compatible with \gls{interactive} performances. % \adnote{Maybe define what you mean by 'interactive' and 'real-time' at some point.}

\subsubsection{HRP-2 -- Car egress (Figure~\ref{fig:car}):}
This scenario is inspired from the Darpa challenge car egress scenario (\url{http://cpc.cx/edH}). HRP-2 has 
to find the contact sequence that allows it to step out of a car.

\begin{figure}
  \centering
  \includegraphics[width=0.5\linewidth]{figures/car}
  \caption{
           Selected frames from the car egress scenario. }
		   \label{fig:car}
\end{figure}

@@

\noindent\textbf{Observations:} The difficulty of this scenario lies in the strong reduction of the reachable workspace induced 
by the extreme proximity of all obstacles. The planner is able to find a sequence, that consists in many steps.
The proximity of the obstacles invalidate a large number of contact candidates because of collisions. To avoid breaking more than one contact between each step, the motion has to be decomposed into a large number of steps (61 in average).
While this scenario is the slowest to solve, the planner still computes a solution \glslink{interactive}{interactively}.
 % \adnote{Maybe define what you mean by 'interactive' and 'real-time' at some point.}

@@

\noindent\textbf{Observations:} In this context, setting up a really important minimum value for $b_0$ is possible due to the high
stability of the HyQ robot, and results in more contact switches, in exchange for safety. The guide path-planning in this scenario takes a few seconds in average, more than
in any other scenarios. This is explained by the necessity of discovering a safe way to ``climb down'' the rubble. In this part of the planning, the constraint that the 4 reachable workspaces of all legs must collide with the environment at all times is hard to respect, but enforces the equilibrium of HyQ. %\adnote{Why do not relax this constraint and require only 3 legs?} 
Again, the computation times remain however \gls{interactive}.

@@

\noindent\textbf{Observations:} Despite the apparent simplicity of the scene, this scenario is a hard case for a contact planner.
While finding a guide path above the hole is easy for the guide planner, finding a sequence of contacts that allows for equilibrium is not trivial.
Second, the narrow bridge is hard both for the planner and the contact generator: to make sure that equilibrium is preserved along the traversal,
the bridge must be approached with the appropriate angle.
The difficulty is illustrated in Figure~\ref{fig:HyQ_obs}, where several feet rearrangements are required to cross the hole (although the video shows this best).
The planner however succeeds in finding a feasible sequence in the end, again with \gls{interactive} computation times.

@@

\noindent\textbf{Observations:} This scenario is designed to illustrate concretely the computation times of the planner.
In the video, the footsteps indicating the contact sequence appear at the average speed of their computation (including the guide-path planning).

@@

\subsection{Influence of the parameters} \label{sec:influence}
This subsection discusses the several factors that influence the outcome of our planner: the root scaling factor $s$, the choice of heuristics for
contact generation, the desired value of the robustness parameter $b_0$, and lastly, the discretization 
of the guide path.

@@

The obtained results for HRP-2 are summarized in Table~\ref{tab:scale}, averaged over all scenes (except for the car egress: in this scenario, 
statistical tests are not really conclusive since we are only interested in a small area of the environment).
As it can be expected, the scaling results in a high increase of the false negatives, while the false positives decrease.
For HRP-2 we decided to set $s^*=1.2$, that results in less than 3 \% of false positives, and was also effective
for the car egress scenario.

@@

\subsubsection{On the robustness equilibrium criterion:} \label{sec:parrob}
Robustness is really important when considering practical applications on the robot, to account 
for the various uncertainties that result from environment and state estimation. However,
maximizing the robustness criterion is often not optimal, because the resulting configurations may be too conservative, thus not favoring the motion. In our experiments, we choose not to maximize the robustness,
but to empirically set a robustness threshold value under which a configuration is not considered to be in
static equilibrium (If no candidate reaches the threshold, instead of failing, the algorithm can eventually return the ``more robust'' configuration
found). Currently for HRP-2, a threshold value of 2 subjectively gives the best results in the considered scenarios, while 10 seems to be a good choice for HyQ. Both values do not
significantly slow down the planning times.

@@

\subsection{Performance analysis} \label{sec:perf}
To analyze performance, for each considered scenario, we ran the planner 1000 times.
We measured the computation time spent in each aspect of the algorithm, and also analyzed the success
rate obtained for each scenario.

>>>>

% !TEX root =  ../main.tex
\section{Results}
\label{sec:results}
In this Section we present some of the results obtained with our planner. The complete sequences computed are shown in the companion video.
Specifically, we demonstrate the planner for two really different robots, in a large variety of environments: the humanoid HRP-2 and the quadruped HyQ.
Finally, a last example suggests possible applications to dexterous manipulation.

At the end of the video, we validate our contact plans by exhibiting a solution to the interpolation problem $\mathcal{P}_3$ for these scenarios.

At the end of this Section, we analyze the influence of the parameters of our framework on the output, and provide the \textit{interactive} computation times obtained in each case.
We also compare the times obtained with HRP-2 with respect to previous works.

@@

\subsection{Description of the scenarios}
In all the scenarios considered, the formulation of the problem is always the same:
a start and goal root configurations are provided as an input of the scenario.
The framework computes the initial contact configuration, and outputs a sequence of contact configurations connecting it to the goal.
In each scenario we detail the contacts involved and the heuristics chosen (either $h_{\textrm{\it EFORT}}$, $h_{vel}$ or $h_{w}$, all of which are defined in the Appendix~\ref{sec:heuristics}).
 %~ and the constraints on the reachable workspaces (for instance in all the scenarios, the reachable workspaces of the legs of HRP-2 are always required to intersect with the environment). 
%~ The companion video presents the complete contact sequence obtained in all these scenarios.

@@

\noindent\textbf{Heuristics:} The manipulability $h_w$ is chosen for the feet; $h_{\textrm{\it EFORT}}$ is chosen for the right arm.
%~ Regarding equilibrium, the video demonstrates two sequences computed for two different threshold values of $b_0$: $0$ and $2$ (Figure~\ref{fig:stair_robust}).

%~ \noindent\textbf{Observations:}
%~ This scenario illustrates best the importance of the equilibrium-robustness criterion.
%~ With a robust approach, more states are required to reach the last step (15 rather than 13 in average).
%~ However, when the last step is reached by both feet, in the nonrobust case the contacts are extremely close to 
%~ the cone limits (Figure~\ref{fig:stair_comp}).
%~ 
%~ 
%~ The geometry of the environment is easily addressed by our planner, and the contact planning is several times faster than real time in this scenario.
%~ 
%~ Again, the interpolation motion between the contact steps is out of the scope of this paper. However it should be noted that the computed plan in this scenario has been executed successfully on the robot (\url{http://youtu.be/YjL-DBQgXwk#t=0m28s}).
%~ 
%~ \begin{figure}
  %~ \centering
  %~ \begin{overpic}[width=0.5\linewidth]{figures/stair_robust}
		%~ \put (17,5) {\small{\color{red}$b_0 = 0.23$}} 
		%~ \put (79,5) {\small{\color{green}$b_0 = 6.16$}} 
	%~ \end{overpic}
  %~ \caption{
           %~ Evaluation of the robustness $b_0$ of two contact configurations. Although in equilibrium, the left configuration is on the verge of slipping.}
		   %~ \label{fig:stair_comp}
%~ \end{figure}

@@

%~ \noindent\textbf{Observations:} The scenario illustrates well the acyclic aspect of the planning. For instance, in the four first frames of Figure~\ref{fig:standing}, we can see that the right foot
%~ is moved twice, with the left foot in between, before the configuration allows HRP-2 to move its hand.
%~ Because the contacts are tried in a FIFO manner, the fact that the output contact sequence is acyclic shows that a cyclic approach (with a finite state machine for instance) is not sufficient
%~ for the computed path. The reason for this is not reachability, but equilibrium. The planning is slower than for the stair scenario (because the contact generation fails more),
%~ though it remains compatible with \gls{interactive} performances. % \adnote{Maybe define what you mean by 'interactive' and 'real-time' at some point.}

\subsubsection{HRP-2 -- Polaris car egress (Figure~\ref{fig:car}):}
This scenario is inspired from the Darpa challenge car egress scenario (\url{http://cpc.cx/edH}). HRP-2 has 
to find the contact sequence that allows it to step out of the Polaris car.

\begin{figure}
  \centering
  \includegraphics[width=1\linewidth]{figures/polaris}
  \caption{
           Selected frames from the polaris egress scenario. }
		   \label{fig:car}
\end{figure}

@@

%~ \noindent\textbf{Observations:} The difficulty of this scenario lies in the strong reduction of the reachable workspace induced 
%~ by the extreme proximity of all obstacles. The planner is able to find a sequence, that consists in many steps.
%~ The proximity of the obstacles invalidate a large number of contact candidates because of collisions. To avoid breaking more than one contact between each step, the motion has to be decomposed into a large number of steps (61 in average).
%~ While this scenario is the slowest to solve, the planner still computes a solution \glslink{interactive}{interactively}.

@@

%~ \noindent\textbf{Observations:} In this context, setting up a really important minimum value for $b_0$ is possible due to the high
%~ stability of the HyQ robot, and results in more contact switches, in exchange for safety. The guide path-planning in this scenario takes a few seconds in average, more than
%~ in any other scenarios. This is explained by the necessity of discovering a safe way to ``climb down'' the rubble. In this part of the planning, the constraint that the 4 reachable workspaces of all legs must collide with the environment at all times is hard to respect, but enforces the equilibrium of HyQ. %\adnote{Why do not relax this constraint and require only 3 legs?} 
%~ Again, the computation times remain however \gls{interactive}.

@@

%~ \noindent\textbf{Observations:} Despite the apparent simplicity of the scene, this scenario is a hard case for a contact planner.
%~ While finding a guide path above the hole is easy for the guide planner, finding a sequence of contacts that allows for equilibrium is not trivial.
%~ Second, the narrow bridge is hard both for the planner and the contact generator: to make sure that equilibrium is preserved along the traversal,
%~ the bridge must be approached with the appropriate angle.
%~ The difficulty is illustrated in Figure~\ref{fig:HyQ_obs}, where several feet rearrangements are required to cross the hole (although the video shows this best).
%~ The planner however succeeds in finding a feasible sequence in the end, again with \gls{interactive} computation times.

@@

%~ \noindent\textbf{Observations:} This scenario is designed to illustrate concretely the computation times of the planner.
%~ In the video, the footsteps indicating the contact sequence appear at the average speed of their computation (including the guide-path planning).

@@

\subsection{Influence of the parameters} \label{sec:influence}
This subsection discusses the several factors that influence the outcome of our planner: the root scaling factor $s$, the choice of heuristics for
contact generation, 
%~ the desired value of the robustness parameter $b_0$, 
and lastly, the discretization 
of the guide path.

@@

The obtained results for HRP-2 are shown in Table~\ref{tab:scale}, averaged over all scenes (except for the car egress: in this scenario, 
statistical tests are not really conclusive since we are only interested in a small area of the environment).
As it can be expected, the scaling results in a high increase of the false negatives, while the false positives decrease.
For HRP-2 we decided to set $s^*=1.2$, which results in less than 3 \% of false positives.
%~ , and was also effective for the car egress scenario.

@@

%~ \subsubsection{On the robustness equilibrium criterion:} \label{sec:parrob}
%~ Robustness is really important when considering practical applications on the robot, to account 
%~ for the various uncertainties that result from environment and state estimation. However,
%~ maximizing the robustness criterion is often not optimal, because the resulting configurations may be too conservative, thus not favoring the motion. In our experiments, we choose not to maximize the robustness,
%~ but to empirically set a robustness threshold value under which a configuration is not considered to be in
%~ static equilibrium (If no candidate reaches the threshold, instead of failing, the algorithm can eventually return the ``more robust'' configuration
%~ found). Currently for HRP-2, a threshold value of 2 subjectively gives the best results in the considered scenarios, while 10 seems to be a good choice for HyQ. Both values do not
%~ significantly slow down the planning times.

@@

\subsection{Performance analysis} \label{sec:perf}
To analyze performance, for each considered scenario, we ran the planner 1000 times.
We measured the computation time spent in each aspect of the algorithm, and analyzed their success rate.
